% Document class and basic packages
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{textcase}

% Document setup
\definecolor{headerColor}{RGB}{0,0,0}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.08003pt}

% Font configuration
\input{glyphtounicode}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\renewcommand{\sfdefault}{phv}
\renewcommand{\rmdefault}{ptm}

% Page layout
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom%
\raggedright%
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{headerColor}\titlerule%
\vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{ #2} \\
      \textit{#3} & \textit{ #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
    {\Huge \scshape Pulkit} \\ \vspace{3pt}
    New Delhi, India \\ \vspace{3pt}
    \small 
    \href{https://www.devpulkit.in/}{\raisebox{-0.2\height}\faLink\ \underline{devpulkit.in}} ~
    \href{mailto:kpulkit15234@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{kpulkit15234@gmail.com}} ~
    \href{https://www.linkedin.com/in/pulkitxm}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/pulkitxm}} ~
    \href{https://github.com/Pulkitxm}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/pulkitxm}}
    \vspace{-8pt}
\end{center}

\section{Education}
\resumeSubHeadingListStart%
\resumeSubheading%
{Bachelor of Technology in Computer Science}{Gurugram, Haryana, India}
{Dronacharya College of Engineering}{Oct. 2022 – Present}
\resumeSubHeadingListEnd%

\section{Experience}
\resumeSubHeadingListStart%
\resumeSubheading%
{Full Stack Engineer Intern}{April 2024 - Sept. 2024}
{\href{https://www.datawavelabs.io/}{Datawavelabs}}{Remote, India}
\resumeItemListStart%
\resumeItem{Increased user authentication security by 40\% through implementation of JWT tokens and Google OAuth integration}
\resumeItem{Implemented cloud account integration with AWS, Azure, and GCP, allowing users to connect and manage cloud services within the application.}
\resumeItem{Automated the workflow of running Docker containers for cluster services, providing real-time status updates and improving system efficiency.}
\resumeItem{Improved database query performance by 50\% by implementing SQLAlchemy ORM and optimizing PostgreSQL queries instead of raw sql queries}
\resumeItem{Collaborated in daily standup meetings and effectively managed tasks with minimal supervision, ensuring timely delivery of features.}
\resumeItemListEnd%
\resumeSubHeadingListEnd%
\vspace{-14pt}

\section{Technical Projects}
\vspace{-1pt}
\begin{itemize}[leftmargin=*,itemsep=2pt,parsep=0pt,topsep=0pt,partopsep=0pt]

    \item \textbf{\href{https://deployit.live/}{Deployit}} $|$ \emph{MERN, Typescript, S3, Image Processing with JIMP}\hfill {August 2024}
          \begin{itemize}[leftmargin=*,itemsep=1pt,parsep=0pt,topsep=0pt,partopsep=0pt]
              \item Built a deployment platform enabling users to deploy repositories with a custom
                    slug URL, featuring automated build and deployment processes.
              \item Developed deployment queueing using Redis for efficient task management and
                    streamlined operations.
              \item Enhanced performance and scalability by using CDN to serve assets quickly and
                    reliably.
          \end{itemize}

    \item \textbf{\href{https://image-tweaker.devpulkit.in/}{Image Tweaker}} $|$ \emph{MERN, Typescript, S3, Image Processing with JIMP} \hfill { August 2024}
          \begin{itemize}[leftmargin=*,itemsep=1pt,parsep=0pt,topsep=0pt,partopsep=0pt]
              \item Built an image optimization tool using Node.js, Express.js, and Docker,
                    featuring real-time adjustments and S3 caching for enhanced performance.
              \item Designed a user-friendly interface for diverse image manipulation needs,
                    integrating JIMP for advanced processing capabilities.
          \end{itemize}

    \item \textbf{Vidwave} $|$ \emph{MERN, Typescript, S3, Docker, Video.js (HLS)}\hfill {August 2024}
          \begin{itemize}[leftmargin=*,itemsep=1pt,parsep=0pt,topsep=0pt,partopsep=0pt]
              \item Developed a video streaming platform with upload, transcoding, and streaming
                    capabilities using AWS S3.
              \item Designed automatic video transcoding and HLS streaming for optimal playback,
                    leveraging Redis for efficient queue management.
          \end{itemize}

\end{itemize}
\vspace{-8pt}

\section{Technical Skills}
\begin{itemize}[leftmargin=*,itemsep=2pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item \textbf{Languages:} TypeScript, JavaScript, Python, Java, C++, SQL
    \item \textbf{Backend:} Node.js, Express.js, Hono, FastAPI, GraphQL, REST APIs
    \item \textbf{Frontend:} NextJS, React.js, HTML5, CSS3, Tailwind CSS, Material-UI, Redux, Shadcn/ui
    \item \textbf{DevOps \& Cloud:} Docker, AWS (EC2, S3, CloudFront), Azure, CI/CD, GitHub Actions
    \item \textbf{Database \& Cache:} PostgreSQL, MongoDB, Redis, Prisma ORM
    \item \textbf{Testing:} Jest, Cypress, Unit Testing, Integration Testing
    \item \textbf{Tools \& Security:} Git, JWT, OAuth 2.0, Bcrypt
\end{itemize}
\vspace{-7pt}

% \section{Certifications}
% \vspace{-8pt}
% \begin{table}[h!]
%     \renewcommand{\arraystretch}{1.5}
%     \setlength{\tabcolsep}{6pt}
%     \begin{tabularx}{\linewidth}{|X|X|l|l|}
%         \hline
%         \textbf{Certification} & \textbf{Issuing Organization} & \textbf{Date} & \textbf{Link} \\
%         \hline
%         GitHub Foundations & \href{https://github.com}{GitHub} & November, 2024 & 
%         \href{https://www.credly.com/badges/0d980c06-511c-4e3d-a9a7-9973688b34ad}{View} \\
%         \hline
%         Full Stack Open & \href{https://www.helsinki.fi/en}{University of Helsinki} & March, 2024 & 
%         \href{https://studies.cs.helsinki.fi/stats/api/certificate/fullstackopen/en/YOUR-CERT-ID}{View} \\
%         \hline
%     \end{tabularx}
% \end{table}

\section{Leadership \& Achievements}
\begin{itemize}[leftmargin=*,itemsep=2pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item \textbf{ICPC Amritapuri 2023 Regionalist}: Qualified for the regional round of the global programming competition.
    \item \textbf{Chairman \& Web Lead}, Deviators Club: Student-led technical initiative. Hosted a lot of tech events
    \item \textbf{HackKRMU 3.0 AIML Track Prize Winner}: Recognized for innovative AI/ML application.
    \item \textbf{Gurugram University Ideathon Winner}: Secured first place for innovative AI-driven travel solutions, awarded by the Honorable Chief Minister of Haryana.
\end{itemize}

\end{document}